Eddy covariance towers as sentinels of abnormal radioactive material releases

### 2024-11-03 manuscript/manuscript.tex
subheader update

\subsection{Modeling Approach}
We processed each data file by 1) excluding nighttime measurements based on photosynthetic photon flux density (PPFD > 100 µmol m-2 s-1) or net solar radiation (netrad > 0 $W/m^2$) and 2) defining an “event period” following the publicly released date of the abnormal release. We focused on the following variables as potentially containing a signature of the release : carbon dioxide, carbon dioxide flux (fc), latent heat (le), and sensible heat flux (h). Conversely, the following were treated as independent explanatory variables: wind speed, precipitation, atmospheric pressure, relative humidity, photosynthetic photon flux density, air temperature, and net radiation. Additionally, we used wind direction data from the eddy flux towers to determine when or if any released material might plausibly reach a particular location. Each of these variables were recorded by the flux tower instrumentation at a 30 minute (min) interval barring any gaps due to missing data.

>>>>

\subsection{Statistical Approach}
We processed each data file by 1) excluding nighttime measurements based on photosynthetic photon flux density (PPFD > 100 µmol m-2 s-1) or net solar radiation (netrad > 0 $W/m^2$) and 2) defining an “event period” following the publicly released date of the abnormal release. We focused on the following variables as potentially containing a signature of the release : carbon dioxide, carbon dioxide flux (fc), latent heat (le), and sensible heat flux (h). Conversely, the following were treated as independent explanatory variables: wind speed, precipitation, atmospheric pressure, relative humidity, photosynthetic photon flux density, air temperature, and net radiation. Additionally, we used wind direction data from the eddy flux towers to determine when or if any released material might plausibly reach a particular location. Each of these variables were recorded by the flux tower instrumentation at a 30 minute (min) interval barring any gaps due to missing data.
